A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-11-12 manuscript.Rmd
typo fixes manuscript
fix three typos including wrong package name rodoc > redoc

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as R Markdown. That is, we have experienced the case that after writing up the first draft in R Markdown, we eventually had to generate a Word file that, from then on, was used as static file serving as a basis for multiple iterations among the co-authors. Retaining reproduciblity in such situations then requires tedious manual synchronization of files across formats. This annoyance may be reduced with the [`rodoc` package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@redoc], which enables a bidirectional synchronization between Word and R Markdown. Conversions between R Markdown and Word retain all changes and even support Word's track-changes feature.

>>>>

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as R Markdown. That is, we have experienced the case that after writing up the first draft in R Markdown, we eventually had to generate a Word file that, from then on, was used as static file serving as a basis for multiple iterations among the co-authors. Retaining reproduciblity in such situations then requires tedious manual synchronization of files across formats. This annoyance may be reduced with the [`redoc` package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@redoc], which enables a bidirectional synchronization between Word and R Markdown. Conversions between R Markdown and Word retain all changes and even support Word's track-changes feature.
